NumPy---Array Computation for Python

### 2019-12-17 paper.tex
Update outline
Add a few paragraphs about wheel building.

% Wheels build system

% NEP 29 (which releases are supported in rolling window)

@@

% NumPyDoc standard, recent improvements

>>>>

\subsubsection*{Wheels build system}

A Python \emph{wheel}\cite{PEP427} is a standard file format for
distributing Python libraries.  In addition to Python code, a
wheel may include compiled C extensions and other binary data.
This is important, because many libraries, including NumPy,
require a C compiler and other build tools to build the software
from the source code, making it difficult for many users to install
the software on their own.  The introduction of wheels to the Python
packaging system has made it much easier for users to install
precompiled libraries.

A GitHub repository containing scripts to build NumPy wheels has
been configured so that a simple commit to the repository triggers
an automated build system that creates NumPy wheels for several
computer platforms, including Windows, Mac OSX and Linux.  The wheels
are uploaded to a public server and made available for anyone to use.
This system makes it easy for users to install precompiled versions
of NumPy on these platforms.

The technology that is used to build the wheels evolves continually.
At the time this paper is being written, a key component is the
\code{multibuild} suite of tools developed by Matthew Brett and
other developers\cite{multibuild}.  Currently, scripts using
\code{multibuild} are written for the continuous integration
platforms Travis-CI (for Linux and Mac OSX) and Appveyor
(for Windows).

\subsubsection*{NEP 29}

@@

\subsubsection*{NumPyDoc standard}

% recent improvements
